---
title: "Messing Around"
author: "Sam Galloway"
date: "10/28/2020"
output: html_document
---
```{r}

```


```{r check_packages, include = FALSE}
# Installs required packages if they aren't already installed!
  packageList <- c("pdftools","tm","tesseract","tidyverse","tools","sjmisc","tabulizer","readr",
                   "svdialogs")
  for(p in packageList){
    if (!requireNamespace(p)) {
      install.packages(p)
    }
  }
```

```{r setup, include=FALSE}
library(pdftools)
library(tm)
library(tesseract)
library(tidyverse)
library(tools)
library(sjmisc)
library(tabulizer)
library(readr)
library(svDialogs)
```

The following is my code that reads in the pdf and then splits it up into multiple columns appropriately. 

```{r}
src <- ""

QTD_COLUMNS <- 2
read_text <- function(text) {
  result <- ''
  #Get all index of " " from page.
  lstops <- gregexpr(pattern =" ",text)
  #Puts the index of the most frequents ' ' in a vector.
  stops <- as.integer(names(sort(table(unlist(lstops)),decreasing=TRUE)[1:2]))
  #Slice based in the specified number of colums (this can be improved)
  for(i in seq(1, QTD_COLUMNS, by=1))
  {
    temp_result <- sapply(text, function(x){
      start <- 1
      stop <-stops[i] 
      if(i > 1)            
        start <- stops[i-1] + 1
      if(i == QTD_COLUMNS)#last column, read until end.
        stop <- nchar(x)+1
      substr(x, start=start, stop=stop)
    }, USE.NAMES=FALSE)
    result <- append(result, temp_result)
  }
  result
}
```

```{r}
#Setting this equal to the pdf I've been messing around with the most initially for now, in full one will change to a folder multiple pdfs are stored in
txt <- pdf_text("Warren et al. 1986 The Influence of Livestock Trampling under Intensive Rotation Grazing on Soil Hydrologic Characteristics (C).pdf")
result <- ''
finalPDF <- NULL
for (i in 1:length(txt)) { 
  result=NULL
  #Goes through every page of the pdf, splits them appropriately, and then appends them to a final PDF (that's still appropriately seperated by page, for efficiency's sake of when we only need to look at first page)
  page <- txt[[i]]
  t1 <- unlist(strsplit(page, "\r\n")) 
  maxSize <- max(nchar(t1))
  t1 <- paste0(t1,strrep(" ", maxSize-nchar(t1)))
  result = append(result,read_text(t1))
  finalPDF[[i]] = result
}
finalPDF <- finalPDF %>% lapply(trimws)
```


```{r}
##Here, I get the first page of the PDF, so that it's faster to extract data about the title/authors/journal
firstPage <- finalPDF[[1]]
```

Currently assumes all authors are in caps for simplicity's sake, will be expanded upon.
```{r}
Title <- ""

for (i in 1:length(firstPage)) {
  #Looks for the first string where there are at least five consecutive capital letters, as this is where it's currently assumed the author is. If it reaches this, it breaks
  if(grepl("[[:upper:]]{5,}",firstPage[i])) {
    break
  }
  #If the line is before the authors, it's presumed to be part of the title, so this information is saved.
  else {
    Title = paste(Title,firstPage[i],sep=" ")
  }
}

Title <- trimws(firstPage)
Title
```

Currently assumes authors are tracked by being all in capital letters, will be expanded upon.
```{r}
#Gets the first string with 5 consecutive capital letters in it, currently assumed to be the authors
Authors <- str_split(grep("[[:upper:]]{5,}",firstPage,value=T)[1],",") %>% lapply(trimws) %>% lapply(toupper)

Authors 
```

```{r}
Journal <- ""

#In a for loop that starts at the end, we look for a string containing the word "Journal"-- needs to be expanded upon more, as since writing this code I found that most of the journals don't actually have "Journal" in their name.
for (i in length(firstPage):1) {
  if (grepl("JOURNAL", result[i])) {
    new <- trimws(result[i])
    #Here, I split it up so that all of the dates that are in the same line are seperated out, so that we're left with only the Journal title.
    Journal <- strsplit(new,split="        ")[[1]][1]
    break
  }
}

Journal
```

Here is a test of how we can use dialogue boxes to verify the information gathered.
```{r}
Journal <- dlgInput("What is the journal's name?", Journal)
```










